---
title: "Data-Organization"
author: "Anna Talucci"
date: "1/21/2021"
output: html_document
---

# Overview

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/

**Data organization** 
Involve converting to plot level varaibles and some cleaning. Create plot_dis for distance on the transect that removes alpha 'a' and 'b' from -25 plots on BP transect.



**Calculate total basla area for plots**
Total Basal area in meteres squared


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
```

# Functions

```{r}
numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 


```

# Site info

```{r}
field_snags = read.csv("../data/original_csv/17Feb2017_Part12_v1_cwd_snag.csv")
field_soil = read.csv("../data/original_csv/17Feb2017_Part12_v1_ surface_seed.csv")
```

## Look at data
```{r}
head(field_snags)
head(field_soil)
```
```{r}
unique(field_snags$Plot_ID)
unique(field_soil$Plot_ID)
```

```{r}
nrow(field_snags)
nrow(field_soil)
```

# Select columns of interest
```{r}
field_snags1 = field_snags %>% dplyr::select(plot:Plot_ID, vis_FE, Fire_id)
head(field_snags1)
```

```{r}
field_soil1 = field_soil %>% dplyr::select(plot:vis_FE, Fire_id:soil.sur, duff.dpth)
head(field_soil1)
```

# Merge data frames
```{r}
field_plot = merge(field_snags1, field_soil1, by= c("plot", "Plot_ID", "Fire_id"))
field_plot
```




```{r eval=FALSE, include=FALSE}
write.csv(field_plot,"../outputs/field_subset/site_info_uav.csv", row.names = FALSE)
```